---
title: "BasicParameters"
author: "Matt Denwood"
date: "20/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(eggSim)
```

```{r}

budget <- 1200
reduction <- 0.2

# Decide on variability partitions:
cv_between <- 1.5
cv_within <- 0.75
cv_slide <- 0.25
cv_reduction <- 0
# Overall k is about 0.23 - seems sensible??
combined_k(cv_between, cv_within, cv_slide, cv_reduction)

#cv_between <- 1/0.4^0.5
#cv_within <- 1/2^0.5
#cv_slide <- 0
#cv_reduction <- 0
# Overall k is about 0.23 - seems sensible??
#combined_k(cv_between, cv_within, cv_slide, cv_reduction)

# Simulate data:
simdatagp <- cgpDataSim(R=10^3, N=budget, reduction=reduction, community_mean=24, cv_between=cv_between, cv_within=cv_within, cv_slide=cv_slide, cv_reduction=cv_reduction, grams=1/24)

gpmeans <- design_means(simdatagp, budget=budget, count=TRUE)

comnrs <- gpmeans %>%
  count(Design, Communities)
ggplot(comnrs, aes(x=Design, y=n, fill=factor(Communities))) +
  geom_col()

ggplot(gpmeans %>% filter(Communities > 0), aes(x=Design, y=ScreenProp)) +
  geom_boxplot()

ggplot(gpmeans %>% filter(Communities > 0), aes(x=Design, y=ArithmeticEfficacy)) +
  geom_hline(yintercept=100*(1-reduction)) +
  geom_boxplot()

ggplot(gpmeans %>% filter(Communities > 0), aes(x=ArithmeticEfficacy, col=Design)) +
  stat_ecdf()

gpmeans %>%
  mutate(Success = 100 * sum(Communities > 0) / n()) %>%
  filter(Communities > 0) %>%
  group_by(Design, Success) %>%
  summarise(ScreenProp = mean(ScreenProp), Mean = mean(ArithmeticEfficacy), Median = median(ArithmeticEfficacy), Variance = var(ArithmeticEfficacy), .groups='drop')
```



## Full simulation

I have written a wrapper function that allows us to generate the figure 1 we planned.  Here are some reasonable parameter estimates (assuming 3 communities - this can be changed):

```{r}
# Number of replicates:
R <- 250
# Reduction (either geometric or arithmetic mean, depending on LP vs GP) - can be vectorised:
reduction <- seq(0,1,by=0.05)
# Community means (either geometric or arithmetic mean, depending on LP vs GP):
community_mean <- 24
```

But these are currently a complete guess!!!

```{r}
# CV between individuals (vectorised to correspond to community means above):
cv_between <- 1.5
# CV within individuals (day-to-day variation):
cv_within <- 0.75
# CV within individual and day (slide-to-slide variation):
cv_slide <- 0.25
# Variation in efficacy between individuals:
cv_reduction <- 0

# The lengths of these must match:
stopifnot(length(cv_between)==length(community_mean))

# The budget:
budget <- 1200
```

To produce the output (takes a while):

```{r}
t <- Sys.time()
results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=FALSE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
difftime(Sys.time(), t)

ggplot(results %>% filter(!is.na(Bias)), aes(x=Target, y=Bias, ymin=LCI, ymax=UCI, col=Design)) +
  geom_hline(yintercept=0) +
  geom_errorbar(position='dodge') +
  geom_line() +
  geom_point() +
  facet_wrap(~ Set, scales='free_y') +
  xlab('True efficacy (arithmetic or geometric mean as indicated)')
```

Note that the NS estimates are removed from the top right and bottom left plots because I am using this method to estimate the true values (the assumption is that the bias would be zero though).

Or to look at variance of the estimator:

```{r}
ggplot(results, aes(x=Target, y=Variance, col=Design)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ Set, scales='free_y') +
  xlab('True efficacy (arithmetic or geometric mean as indicated)')
```

Worth noting that the variance of the geometric mean estimator is much smaller than the arithmetic (which I think is Jan's point!)
