---
title: "Data Simulation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library('tidyverse')
theme_set(theme_light())
library('eggSim')
```

## Parameters

```{r}
# Number of individuals:
N <- 100
# Number of bootstrap simulations:
R <- 10^4

# Arithmetic mean eggs per gram in the pre- and post-treatment data:
mus <- c(1000, 100)
# Extra-Poisson coefficient of variation (ratio of standard deviation to the mean):
cvs <- c(1.5, 2)
# Extra-Poisson correlation:
cor <- 0.33

# Equivalent arithmetic and geometric mean efficacies for reference:
efficacies <- ERRparameters(mus[1], mus[2], cvs[1], cvs[2], cor, TRUE)$efficacies
efficacies
```


## Simulating gamma-Poisson data

For efficiency simulate a single big dataset with N * R observations, then do a count using a standard McMaster:

```{r}
simdata <- gpDataSim(N*R, mus[1], mus[2], cvs[1], cvs[2], cor) %>%
  mutate(Replicate = rep(1:R, each=N)) %>%
  mutate(preCount = rpois(n(), preLambda/50), postCount = rpois(n(), postLambda/50))
```

Verify that we can recover the simulation parameters:

```{r}
mean(simdata$preLambda)
mus[1]
```

```{r}
mean(simdata$postLambda)
mus[2]
```

```{r}
sd(simdata$preLambda)/mean(simdata$preLambda)
sd(simdata$postLambda)/mean(simdata$postLambda)
cvs
```

```{r}
cor(simdata$preLambda, simdata$postLambda)
cor
```

```{r}
gammadata <- simdata
```


## Simulating lognormal-Poisson data

For efficiency simulate a single big dataset with N * R observations:

```{r}
simdata <- lpDataSim(N*R, mus[1], mus[2], cvs[1], cvs[2], cor) %>%
  mutate(Replicate = rep(1:R, each=N)) %>%
  mutate(preCount = rpois(n(), preLambda/50), postCount = rpois(n(), postLambda/50))
```

Verify that we can recover the simulation parameters:

```{r}
mean(simdata$preLambda)
mus[1]
```

```{r}
mean(simdata$postLambda)
mus[2]
```

```{r}
sd(simdata$preLambda)/mean(simdata$preLambda)
sd(simdata$postLambda)/mean(simdata$postLambda)
cvs
```

This is different to the gamma Poisson data as the correlation is on the log scale:

```{r}
cor(log(simdata$preLambda), log(simdata$postLambda))
cor
# cf:
cor(simdata$preLambda, simdata$postLambda)
```

```{r}
lnormdata <- simdata
```


## Analysing the gamma data

Basic analysis based on underlying lambda values for simplicity:

```{r}
summaries <- gammadata %>%
  group_by(Replicate) %>%
  summarise(arithmetic = 100*(1-mean(postLambda)/mean(preLambda)), geometric = 100*(1-exp(mean(log(postLambda))-mean(log(preLambda))))) %>%
  gather(type, value, -Replicate)
```

```{r}
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['gamma',], lty='dashed') +
  geom_boxplot()
```


Same looking at counts (arithmetic mean only - we could add an arbitrary constant for the geometric mean):

```{r}
summaries <- gammadata %>%
  group_by(Replicate) %>%
  summarise(type='arithmetic', value = 100*(1-mean(postCount)/mean(preCount)))
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['gamma','arithmetic'], lty='dashed') +
  geom_boxplot()
```


And showing the bias in arithmetic mean if we only take pre-treatment positives:

```{r}
summaries <- gammadata %>%
  filter(preCount > 0) %>%
  group_by(Replicate) %>%
  summarise(type='arithmetic', value = 100*(1-mean(postCount)/mean(preCount)))
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['gamma','arithmetic'], lty='dashed') +
  geom_boxplot()
```


## Analysing the lognormal data

Basic analysis based on underlying lambda values for simplicity:

```{r}
summaries <- lnormdata %>%
  group_by(Replicate) %>%
  summarise(arithmetic = 100*(1-mean(postLambda)/mean(preLambda)), geometric = 100*(1-exp(mean(log(postLambda))-mean(log(preLambda))))) %>%
  gather(type, value, -Replicate)
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['lognormal',], lty='dashed') +
  geom_boxplot()
```

Same looking at counts (arithmetic mean only - we could add an arbitrary constant for the geometric mean):

```{r}
summaries <- lnormdata %>%
  group_by(Replicate) %>%
  summarise(type='arithmetic', value = 100*(1-mean(postCount)/mean(preCount)))
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['lognormal','arithmetic'], lty='dashed') +
  geom_boxplot()
```


And showing the bias in arithmetic mean if we only take pre-treatment positives:

```{r}
summaries <- lnormdata %>%
  filter(preCount > 0) %>%
  group_by(Replicate) %>%
  summarise(type='arithmetic', value = 100*(1-mean(postCount)/mean(preCount)))
ggplot(summaries, aes(x=type, y=value)) +
  geom_hline(yintercept = efficacies['lognormal','arithmetic'], lty='dashed') +
  geom_boxplot()
```

## TODO

We want to look at the bias vs mean, cv, correlation and egg detection thresholds...
