---
title: "SanityChecks"
author: "Matt Denwood"
date: "19/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library('tidyverse')
theme_set(theme_light())
library('eggSim')
```

## Test some special cases to ensure the code is correct

Fixed parameters

```{r}
R <- 100
```

### Simplest case

Start with 0% efficacy and a single community

```{r}
reduction <- 1
community_mean <- 1000
```

And zero extra-Poisson variation:

```{r}
# CV between individuals (vectorised to correspond to community means above):
cv_between <- 0
# CV within individuals (day-to-day variation):
cv_within <- 0
# CV within individual and day (slide-to-slide variation):
cv_slide <- 0
# Variation in efficacy between individuals:
cv_reduction <- 0

# The lengths of these must match:
stopifnot(length(cv_between)==length(community_mean))

# The number of individuals used for each design type:
N = c(NS=600, SS=109, SSR1=100, SSR2=92, SSR3=95)
```

Should all have zero bias and zero variance:

```{r}
results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=FALSE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

Should all have zero bias and the same (Poisson plus log_constant) variance within design and data:

```{r}
results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=TRUE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

Now assume all CV is between individuals.  Bias and variance should still be zero without counts:

```{r}
cv_between <- 1
cv_within <- 0
cv_slide <- 0
cv_reduction <- 0

results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=FALSE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

Adding counts adds some bias for  the geometric means due to the log_constant:

```{r}
results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=TRUE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

Now assume all variance is at the slide level.  Now we get bias for everything except the NS method:

```{r}
cv_between <- 0
cv_within <- 0
cv_slide <- 1
cv_reduction <- 0

results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=FALSE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

Now assume all variance is at the day-to-day level.  We should not get bias for the retest methods:

```{r}
cv_between <- 0
cv_within <- 1
cv_slide <- 0
cv_reduction <- 0

results <- eggSim(reduction, N, community_mean, cv_between, cv_within, cv_slide, cv_reduction, count=FALSE, log_constant=if(count) 1 else 0, screen_threshold = 0, edt=24)
results %>% select(Design, Set, Bias, Variance)
```

```{r}
maxN <- 10^3
data <- cgpDataSim(R, maxN, reduction, community_mean, cv_between, cv_within, cv_slide, cv_reduction, overall_mean = mean(community_mean), edt=24)
data %>% filter(Community==1, Individual==1, Replicate==1)
```

